A Switching Planner for Combined Task and Observation Planning

### 2011-04-21 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
Hi Moritz, I have merged the material I think we should have added to the paper...

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\graphicspath{{plots/}}
\include{macros}%

\nocopyright

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

@@

\title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}
\setcounter{secnumdepth}{0}

@@

%% partial observability

%% In cooperation with execution monitoring, it must perform repair
%% and/or replanning in order to seamlessly accommodate exogenous events,
%% changing objectives, and the underlying unpredictability of the
%% environment.

%% Realistic robot planning problems in uncertain environments often
%% require achieving tasks while also finding out about the
%% world. Because the world state cannot be observed directly, these
%% problems are naturally represented as partially observable Markov
%% decision problems (POMDPs). However, these are typically intractable
%% for realistic problems.
%%

@@

%% \section{Propositional Decision-Theoretic Planning}
%% \input{prop-dtp.tex}

@@

>>>>

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{tabularx}
\graphicspath{{plots/}}
\include{macros}%

%%\nocopyright

\pdfinfo{
/Title (A Switching Planner for Combined Task and Observation Planning)
% /Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author ()}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

@@

\title{A Switching Planner for Combined Task and Observation Planning}
\author{
Moritz G{\"o}belbecker \\ University of Freiburg, Germany\\
\{goebelbe\}@informatik.uni-freiburg.de
\And
Charles O. Gretton, Richard Dearden,\\
University of Birmingham, United Kingdom\\
\{c.gretton,R.W.Dearden\}@cs.bham.ac.uk} 
\setcounter{secnumdepth}{0}

@@

@@

\section{Propositionally Factored Decision-Theoretic Planning}
\input{prop-dtp.tex}

@@

\textbf{Acknowledgements}: The research leading to these results has
received funding from the European Community's Seventh Framework
Programme [FP7/2007-2013] under grant agreement No. 215181, CogX.

### 2011-04-21 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
typo
Hi Moritz, I have merged the material I think we should have added to the paper...

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session applies a single entropy reduction action,
whose execution can provide evidence regarding the truth value of a
{\em relevant} assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

We evaluate our approaches in robot exploration tasks from home and
office environments. Spatially, these consist of {\em rooms}
(office/kitchen/etc), and an underlying topological map over
smaller areas of space, called {\em places}, and connectivity between
those. The mobile {\em robot} and {\em visual objects} inhabit the
topological places. Objects indicate the category of space they
inhabit -- e.g., spoons are likely to be in kitchens. By examining
view cones at places for particular objects, the robot is able to: (1)
categorise space at high (room) and low (place) levels, and (2) find
objects for the user, exploiting information about object
co-occurrence and room categories for efficiency. Also, in the
presence of a person, the robot can ask about the category of the
current room.

We compare switching to the {\em baseline} in several realistic
tasks, with the number of rooms ranging from 3 (12-places, 16-objects,
$|$states$|$ $>10^{21}$) to 6 (26-places, 21-objects, $|$states$|$
$>10^{36}$). We also compare those systems with near optimal policies
computed using Smith's {\sc zmdp} for small 2 room problems (4-places,
3-objects, $|$states$|$ $\simeq 5000$). Our evaluation considers 3
levels of reliability in sensing: {\em reliable} sensors have a $.1$
probability of a false negative, {\em semi-reliable} have a chance of
$0.3$ of false negative and $0.1$ of false positive, and {\em noisy}
sensors with probabilities of $0.5$ and $0.2$ respectively. Each
object class is assigned one sensor model -- e.g. cornflakes may be
harder to detect than refrigerators. We performed several experiments
with different levels of reliability for sensing the target object(s),
while keeping sensing models for non-target objects constant.

@@

Our evaluation examines DT sessions with initial belief-states
admitting between 20 and 100 abstract states with non-zero
probability. We run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds)\footnote{All
experiments were conducted on a 2.66GHz Intel Xeon X5355 using one CPU
core.}. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor). The exception occurs for
items f and g of Figure~\ref{fig:results-quality}, where we report
expected discounted rewards (not plan costs).

>>>>

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. Since most of the problems we consider are much larger than
any available DT planner can solve directly, for comparison purposes
we also implemented a simple dual-mode replanning baseline
approach. Here, when a switching action is scheduled for execution the
DT session applies a single entropy reduction action, whose execution
can provide evidence regarding the truth value of a relevant
assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

We evaluate our approaches in robot exploration tasks from home and
office environments. Spatially, these consist of {\em rooms}
(office/kitchen/etc), and an underlying topological map over
smaller areas of space, called {\em places}, and connectivity between
those. The mobile {\em robot} and {\em visual objects} inhabit the
topological places. Objects indicate the category of space they
inhabit---e.g., spoons are likely to be in kitchens. By examining
view cones at places for particular objects, the robot is able to: (1)
categorise space at high (room) and low (place) levels, and (2) find
objects for the user, exploiting information about object
co-occurrence and room categories for efficiency. Also, in the
presence of a person, the robot can ask about the category of the
current room.

We compare switching to the baseline in several realistic
tasks, with the number of rooms ranging from 3 (12-places, 16-objects,
$|$states$|$ $>10^{21}$) to 6 (26-places, 21-objects, $|$states$|$
$>10^{36}$). We also compare those systems with near optimal policies
computed using Smith's {\sc zmdp} for small 2 room problems (4-places,
3-objects, $|$states$|$ $\simeq 5000$). Our evaluation considers 3
levels of reliability in sensing: {\em reliable} sensors have a $.1$
probability of a false negative, {\em semi-reliable} have a chance of
$0.3$ of false negative and $0.1$ of false positive, and {\em noisy}
sensors with probabilities of $0.5$ and $0.2$ respectively. Each
object class is assigned one sensor model---e.g. cornflakes may be
harder to detect than refrigerators. We performed several experiments
with different levels of reliability for sensing the target object(s),
while keeping sensing models for non-target objects constant.

@@

Our evaluation examines DT sessions with initial belief-states
admitting between 20 and 100 abstract states with non-zero
probability. We run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds)\footnote{All
experiments were conducted on a 2.66GHz Intel Xeon X5355 using one CPU
core.}. The continual planning times are reported in
Fig.~\ref{fig:results-time}, and the quality data in
Fig.~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor). The exception occurs for
items f and g of Fig.~\ref{fig:results-quality}, where we report
expected discounted rewards (not plan costs).
